Stable individual differences in strategies within, but not between, visual search tasks

### 2019-05-28 Manuscript/manuscript.tex
added citation of Hedge et al 2018
changing to Sage template

\RequirePackage{fix-cm}
\documentclass[a4paper, man, natbib, floatsintext]{apa6}

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
% \usepackage{lineno}
% \usepackage{hyperref}
\usepackage{graphicx}

% \linenumbers
%%%% Article title to be placed here
\title{Stable individual differences in strategies within, but not between, visual search tasks}
\shorttitle{Differences in search}
\fiveauthors{A. D. F. Clarke}{J. L. Irons}{W. James}{A. B. Leber}{A. R. Hunt}

\fiveaffiliations{Department of Psychology, University of Essex, Colchester, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}

\abstract{
A striking range of individual differences has recently been reported in three different visual search tasks. These differences in performance can be attributed to strategy, that is, the efficiency with which participants control their search to complete the task quickly and accurately. Here we ask if an individual's strategy and performance in one search task is correlated with how they perform in the other two. We tested 64 observers and found that even though the test-retest reliability of the tasks was high, an observer's performance and strategy in one task was not predictive of their behaviour in the other two. These results suggest search strategies are stable over time, but context-specific. To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context.}

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
\caption{Example stimulus from the (a) \textit{split-half line segment} (SHLS), (b) \textit{adaptive choice visual search} (ACVS) and (c) \textit{mouse click foraging task} (MCFT) paradigms.}
\label{fig:exampleStimuli}
\end{figure}

@@

The methods and planned analysis for this study were registered on the Open Science Framework\footnote{\url{https://osf.io/scv4u/}} before data collection started.

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only). (d) Initial search strategy correlates with reaction times in both sessions. Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
\label{fig:splithalf_summary}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/acvs_opt_rt}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/mcft_rl_rt}}
\caption{Correlation between strategy and reaction times for (a) ACVS and (b) MCFT. Each point represents a participant.}
\label{fig:acvs_mcft_summary}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=6.5cm]{../Scripts/scratch/cor_comparison.pdf}
\caption{The between- and within-task correlations for the three different search tasks. The bars indicate the $95\%$ confidence intervals for Pearson's correlation coefficient. Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}). Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy.}
\label{fig:all_the_cor}
\end{figure}

@@

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually.

@@

\bibliography{literature}

>>>>

\documentclass[Afour, sageh, times]{sagej}
% \RequirePackage{fix-cm}
% \documentclass[a4paper, man, natbib, floatsintext]{apa6}

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
% \usepackage{lineno}
% \usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}

% \linenumbers
%%%% Article title to be placed here
\title{Stable individual differences in strategies within, but not between, visual search tasks}
\runninghead{Clarke et al.}
\author{A. D. F. Clarke\affilnum{1} and J. L. Irons\affilnum{2} and W. James\affilnum{3} and A. B. Leber\affilnum{2} and A. R. Hunt\affilnum{3}}

\affiliation{\affilnum{1}Department of Psychology, University of Essex, Colchester, UK \\ 
\affilnum{2}Department of Psychology, The Ohio State University, Columbus, USA \\ 
\affilnum{3}School of Psychology, University of Aberdeen, Aberdeen, UK}

\corrauth{Alasdair D. F. Clarke, Department of Psychology, University of Essex, Colchester, UK.}

\email{a.clarke@essex.ac.uk}

\begin{abstract}
A striking range of individual differences has recently been reported in three different visual search tasks. These differences in performance can be attributed to strategy, that is, the efficiency with which participants control their search to complete the task quickly and accurately. Here we ask if an individual's strategy and performance in one search task is correlated with how they perform in the other two. We tested 64 observers and found that even though the test-retest reliability of the tasks was high, an observer's performance and strategy in one task was not predictive of their behaviour in the other two. These results suggest search strategies are stable over time, but context-specific. To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context.
\end{abstract}

@@

\begin{figure*}
\centering
\subfigure[][]{\includegraphics[height=5cm]{figures/split-half.png}}
\subfigure[][]{\includegraphics[height=5cm]{figures/adaptive.png}}
\subfigure[][]{\includegraphics[height=5cm]{figures/foraging.png}}
\caption{Example stimulus from the (a) \textit{split-half line segment} (SHLS), (b) \textit{adaptive choice visual search} (ACVS) and (c) \textit{mouse click foraging task} (MCFT) paradigms.}
\label{fig:exampleStimuli}
\end{figure*}

@@

The methods and planned analysis for this study were registered on the Open Science Framework\endnote{https://osf.io/scv4u/} before data collection started.

@@

\begin{figure*}
\centering
\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only). (d) Initial search strategy correlates with reaction times in both sessions. Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
\label{fig:splithalf_summary}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure[][]{\includegraphics[width=6cm]{../Scripts/scratch/acvs_opt_rt}}
\subfigure[][]{\includegraphics[width=6cm]{../Scripts/scratch/mcft_rl_rt}}
\caption{Correlation between strategy and reaction times for (a) ACVS and (b) MCFT. Each point represents a participant.}
\label{fig:acvs_mcft_summary}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=10cm]{../Scripts/scratch/cor_comparison.pdf}
\caption{The between- and within-task correlations for the three different search tasks. The bars indicate the $95\%$ confidence intervals for Pearson's correlation coefficient. Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}). Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy.}
\label{fig:all_the_cor}
\end{figure*}

@@

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually. Indeed, we find that the visual search tasks under consideration here compare favourably to other cognitive psychology paradigms, such as Erkison Flanker and Posner Cueing tasks in terms of test-retest reliability \citep{hedge2018}.

@@

\bibliographystyle{sageh}
\bibliography{literature}
